%!TEX TS-program = xelatex

\documentclass {article}

\input {commonpackages.tex}

\setmainfont {Noto Serif}
\setmonofont[Scale=0.8]{Source Code Pro}

\input {lststyles.tex}
\begin {document}

\title {Popchain mainnet audit report}
\input {reportauthor.tex}
\maketitle

\clearpage
\section{Target of analysis}

\begin{itemize}
\item Full project except for BerkeleyDB and libboost component
\end{itemize}

\section{Analysis method}

\begin{itemize}
\item Full project static analysis using Synopsis® Coverity® Scan
\item Manual code inspection
\end{itemize}

\section{Analysis result}
\subsection{Static analysis using Synopsis® Coverity® Scan - High impact issues}
\subsubsection{CID 242525 - Pointer to local outside scope (use-after-free)}
In \texttt{src/main.cpp:AddInvalidSpendsToMap}, reference to 'publicSpend' local variable
is used after 'publicSpend' is freed from the stack. It can be lead to data
corruption.

\lstinputlisting [style=customc, firstline=2473, lastline=2501]{Popchain/src/main.cpp}

\subsubsection{CID 242511 - Resource leak}
In \texttt{src/wallet/wallet.cpp:CWallet::AutoCombineDust}, 'coinControl' is dynamically
allocated but not freed when coinControl->HasSelected() is false. It may lead to
a memory leak which can disrupt stability.

\lstinputlisting [style=customc, firstline=3388, lastline=3437]{Popchain/src/wallet/wallet.cpp}

\subsubsection{CID 242479 - Pointer to local outside scope (use-after-free)}
In \texttt{src/miner.cpp:CreateNewBlock}, reference to 'publicSpoend' and 'spendObj'
member variable is used after 'publicSpend' and 'spendObj' is freed from the
stack. It can be lead to data corruption.

\lstinputlisting [style=customc, firstline=101, lastline=392]{Popchain/src/miner.cpp}

\subsubsection{CID 242476 - Resource leak}
In \texttt{src/wallet/rpcwallet.cpp:serchdzpch}, dzpchThreads is dynamically allocated
but not freed before control leaves the function. It will cause a memory leak
which can disrupt stability.

\lstinputlisting [style=customc, firstline=3632, lastline=3680]{Popchain/src/wallet/rpcwallet.cpp}

\subsubsection{CID 242474 - Resource leak}
In \texttt{src/torcontrol.cpp:ReadBinaryFile}, the file is not properly closed if file
descriptor encountered an error. It can cause file descriptor leak which can
lead to system instability.

\lstinputlisting [style=customc, firstline=370, lastline=389]{Popchain/src/torcontrol.cpp}

\subsubsection{CID 242447 - Uninitialized local variable}
In \texttt{src/spork.cpp:SetPrivKey} uses an uninitialized local variable to test spork
signer. It may lead to an undesirable result. It is strongly advised to use a
properly initialized object.

\lstinputlisting [style=customc, firstline=255, lastline=270]{Popchain/src/spork.cpp}

\subsubsection{CID 186065 - Out-of-bounds access}
In \texttt{src/pubkey.cpp:CPubKey::Derive} incorrectly indexes pubkey array which leads to access
invalid position(ptr+33 > ptr+32). It may lead into severe data corruption.

\lstinputlisting [style=customc, firstline=231, lastline=251]{Popchain/src/pubkey.cpp}

\subsection{Static analysis using Synopsis® Coverity® Scan - Medium impact issues}
\subsubsection{CID 242536 - Dereference after null check}
In \texttt{src/rpc/budget.cpp:preparebudget}, pindexPrev can be null in a special case.
Though it will not cause a practical problem in production due to its special
condition requirement, it is good to fix this problem to improve code quality.

\lstinputlisting [style=customc, firstline=52, lastline=110]{Popchain/src/rpc/budget.cpp}

\subsubsection{CID 242518 - Dereference after null check}
In \texttt{src/zpch/zpchwallet.cpp:CzPCHWallet::SyncWithChain}, in case of
pindex is null (some special condition is required), it can cause wallet crash.

\lstinputlisting [style=customc, firstline=182, lastline=281]{Popchain/src/zpch/zpchwallet.cpp}

\subsubsection{CID 242507 - Explicit null dereferenced}
In \texttt{src/zpch/zpchwallet.cpp:CzPCHWallet::SyncWithChain}, in special case
if \texttt{mapBlockIndex.count(hashBlock)} is zero, \texttt{pindex} will be
null. In this case, it will lead to wallet crash.

\lstinputlisting [style=customc, firstline=182, lastline=281]{Popchain/src/zpch/zpchwallet.cpp}

\subsubsection{CID 242505 - Explicit null dereferenced}
In \texttt{src/main.cpp:AcceptBlock}, in special case when handling genesis
block and zerocoin is active, it will lead into null pointer dereference. In
this case, it will lead to a wallet crash.

\lstinputlisting [style=customc, firstline=182, lastline=281]{Popchain/src/zpch/zpchwallet.cpp}

\subsubsection{CID 242494 - Dereference after null check}
In \texttt{src/rpc/budget.cpp:submitbudget}, in speical case when handling
genesis block, it can lead into null pointer dereference. In this case, it will
lead to a wallet crash.

\lstinputlisting [style=customc, firstline=147, lastline=237]{Popchain/src/rpc/budget.cpp}

\subsubsection{CID 242485 - Dereference null return value}
In \texttt{src/rpc/rawtransaction.cpp:signrawtransaction}, when wallet is in
regression test mode, there is possibility to crash wallet with crafted request.
This vulnerability will not affect production environment because regression
test cannot be connected to internet but it is good to fix this problem to
improve code quality.

\lstinputlisting [style=customc, firstline=630, lastline=780]{Popchain/src/rpc/budget.cpp}

\subsubsection{CID 242477 - Dereference after null check}
In \texttt{src/main.cpp:ConnectBlock}, in practically impossible case when
wallet tries to connect genesis block to somewhere, it can lead into null
pointer dereference. It is not possible to trigger crash using this problem but
it is good to fix this problem to improve code quality.

\lstinputlisting [style=customc, firstline=3287, lastline=3332]{Popchain/src/main.cpp}

\subsubsection{CID 16467 - Improper use of negative value}
In \texttt{src/allocators.cpp:GetSystemPageSize}, if there is no PAGESIZE
defined in \texttt{limits.h}, it falls back to \texttt{sysconf(3)} syscall. In case of
\texttt{sysconf(3)} fails, it returns negative number which will cause severe
misbehavior of wallet.

\lstinputlisting [style=customc, firstline=31, lastline=44]{Popchain/src/allocators.cpp}

\end {document}
